A Comparison of Different Generation lengths

### 2016-04-04 scrap/contest_data.Rmd
fixed r v data, integrated into remake

---
title: "actual contest data"
author: "John Wilshire"
date: "18 March 2016"
output: html_document
---

@@

```{R}
ggplot(contests, aes(y = atk_start_energy , x = def_start_energy )) + 
  geom_point(aes(col=contests$defence_winner)) + 
  ylab("initial energy of the attacker") + 
  xlab("initial energy of the defender") + 
  scale_colour_discrete(name="Defender Wins")

It looks like a lot of the contests end in death
```{R}
ggplot(contests, aes(y = atk_end_energy , x = def_end_energy )) + 
  geom_point(aes(col=contests$defence_winner)) + 
  ylab("final energy of the attacker") + 
  xlab("final energy of the defender") + 
  scale_colour_discrete(name="Defender Wins")

The intensity function is $c^2$
```{R}
ggplot(contests, aes(x = def_commit, y = atk_commit)) + 
  geom_point(aes(col=contests$defence_winner)) + 
  ylab("commitment of the attacker") + 
  xlab("commitment of the defender") + 
  scale_colour_discrete(name="Defender Wins")

@@

>>>>

---
title: "actual contest data"
author: "John Wilshire"
date: "18 March 2016"
output: pdf_document
---

These plots are from training a population to generation 20, they are to give you guys an example of what we can plot for the contests in a generation.

@@

```{R, echo = FALSE}
ggplot(contests, aes(y = atk_start_energy , x = def_start_energy )) + 
  geom_point(aes(col=contests$defence_winner)) + 
  ylab("initial energy of the attacker") + 
  xlab("initial energy of the defender") + 
  scale_colour_discrete(name="Defender Wins")

ggplot(contests, aes(y = atk_end_energy , x = def_end_energy )) + 
  geom_point(aes(col=contests$defence_winner)) + 
  ylab("final energy of the attacker") + 
  xlab("final energy of the defender") + 
  scale_colour_discrete(name="Defender Wins")

ggplot(contests, aes(x = def_commit, y = atk_commit)) + 
  geom_point(aes(col=contests$defence_winner)) + 
  ylab("commitment of the attacker") + 
  xlab("commitment of the defender") + 
  scale_colour_discrete(name="Defender Wins")

@@

ggplot(contests, aes(x = def_mass, y = def_commit)) + 
  geom_point() + 
  ggtitle("commitment vs mass")

ggplot(contests, aes(x = def_mass/atk_mass, y = def_commit)) + 
  geom_point() + 
  ggtitle("commitment vs mass-ratio")

### 2016-04-04 scrap/contests_accross_patch_areas.rmd
fixed r v data, integrated into remake

---
title: "contests accross patch areas"
author: "John Wilshire"
date: "21 March 2016"
output: pdf_document
---

contests_accross_patch_areas.rmd

@@

```
```{R}
all_contests <- load_contests("~/Documents/scrap/contest_data/contest_logging/")
winners <- load_population("~/Documents/scrap/contest_data/contest_logging/")

@@

```
```{R}
# lots of deaths?
qplot(data = contests_summary, x = patch_area, y = def_death_rate + atk_death_rate)
contests_summary$density <- 500 / conteasts_summary$patch_area
ggplot(contests_summary, aes(x = density, y = number_of_fights)) + geom_point() + scale_y_log10() + scale_x_log10() + geom_smooth(method = lm)

>>>>

---
title: "contests accross patch areas FIXED R_V "
author: "John Wilshire"
date: "21 March 2016"
output: pdf_document
---
FIXED R_V

@@

```
```{R}
all_contests <- load_contests("~/Documents/scrap/contest_data/fixed_r_v/")
winners <- load_population("~/Documents/scrap/contest_data/fixed_r_v/")

@@

```
```{R}
# lots of deaths?
qplot(data = contests_summary, x = patch_area, y = def_death_rate + atk_death_rate)
contests_summary$density <- 500 / contests_summary$patch_area
ggplot(contests_summary, aes(x = density, y = number_of_fights)) +
  geom_point() +
  scale_y_log10() + scale_x_log10() + geom_smooth(method = lm)

### 2016-04-04 scrap/continuous_escalation.Rmd
old data cleanup and scrap changes
fixed r v data, integrated into remake

---
title: "A step towards continuous Contests"
author: "John"
date: "9 February 2016"
output: pdf_document
---

@@

df <- data.frame("Commitment" = commitment, "Intensity" = escalation_curve(commitment))
ggplot(df,  aes( x = Commitment, y = Intensity )) +
  geom_line() +
  ggtitle("Example escalation curve") +
  geom_vline(xintercept = 3) + 
  geom_vline(xintercept = 4) +
  annotate("text",x = 2.8, y = 10, label = "c_ i") +
  annotate("text",x = 3.8, y = 20, label = "c_ j")
```

>>>>

---
title: "A Step Towards Continuous Contests"
author: "John"
date: "9 February 2016"
output: pdf_document
---

@@

df <- data.frame("Commitment" = commitment, "Intensity" = escalation_curve(commitment))
ggplot(df,  aes( x = Commitment, y = Intensity )) +
  geom_line() +
  geom_vline(xintercept = 3) + 
  geom_vline(xintercept = 4) +
  geom_polygon(data = rbind(c(0,0), subset(df, commitment < 3), c(3, 0)), 
               aes(alpha = 0.3, fill = "")) + 
  guides(fill = FALSE, alpha = FALSE) + 
  annotate("text", x = 2.8, y = 10, label = "c_ i") +
  annotate("text", x = 3.8, y = 20, label = "c_ j")

```

### 2016-04-04 scrap/evolution.Rmd
fixed r v data, integrated into remake

---
title: "Evolution plots"
author: "John Wilshire"
date: "18 February 2016"
output:
  pdf_document:
    fig_crop: no
    fig_height: 4
  html_document: default
---

```{r, echo=FALSE}
library(jsonlite)
library(plyr)
library(ggplot2)
source("../R/load_datasets.R")
source("../R/make_plots.R")
```

@@

```{R}
expf10_pop <- load_population("../data/exp_f10/")
expf15_pop <- load_population("../data/exp_f15/")
linf10_pop <- load_population("../data/lin_f10/")
population_plots <- function (what){
  print(pop_values(expf10_pop, what, paste("expf10_pop", what)))
  print(pop_values(expf15_pop, what, paste("expf15_pop", what)))
  print(pop_values(linf10_pop, what, paste("linf10_pop", what)))
}

population_plots("e_0")
population_plots("k")
population_plots("2 * radius * speed")

@@

These plots trace how parameters evolve through generations with coloured by patch area...

```{r}
expf10 <- load_trait_history("../data/exp_f10/")
expf15 <- load_trait_history("../data/exp_f15/")
linf10 <- load_trait_history("../data/lin_f10/")

evolution_plots <- function (what){
  print(trait_evolution_plot(expf10, what, paste("expf10", what)))
  print(trait_evolution_plot(expf15, what, paste("expf15", what)))
  print(trait_evolution_plot(linf10, what, paste("linf10", what)))
}

evolution_plots("mean_k")
evolution_plots("std_k")
evolution_plots("std_e_0")
evolution_plots("num_winners")
evolution_plots("mean_maturation")
evolution_plots("contest_energy")
evolution_plots("search_energy")
evolution_plots("occupying_energy")
evolution_plots("mean_exploration")
evolution_plots("std_exploration")
```

>>>>

---
title: "Evolution plots"
author: "John Wilshire"
date: "18 February 2016"
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE}
library(jsonlite)
library(plyr)
library(ggplot2)
source("~/Documents/contests_model/R/load_datasets.R")
source("~/Documents/contests_model/R/make_plots.R")
```

@@

```{R,, echo=FALSE}

exp_100 <- load_population("~/Documents/contests_model/data/cm_100/")
# linf10_pop <- load_population("../data/lin_f10/")
# exp10_1000_pop <- load_population("../data/exp_f10_1000/")
population_plots <- function (y, x, title=""){
    print(pop_values(exp_100, x, y, paste(title,"exp_100", y)))
}

population_plots("e_0", "patch_area")
population_plots("k", "patch_area")

@@

These plots are against the log of the nest density ie log(nests / patch_area)

```{R, , echo=FALSE}
population_plots("e_0", "log(N / patch_area)","density -> ")
population_plots("k", "log(N / patch_area)", "density -> ")

now the energy plot

```{R, echo=FALSE}
exp_trait_100 <- load_trait_history("~/Documents/contests_model/data/cm_100/")
last <- get_generation(exp_trait_100,499)
energy_pc_plot(last, "patch_area")

This is the with the nest density increasing $\rightarrow$

```{R,, echo=FALSE}

energy_pc_plot(last, "log( 500 / patch_area )")

```{r, echo=FALSE}
# exp_100_trait <- load_trait_history("~/Documents/contests_model/data/cm_100/")
# 
# evolution_plots <- function (what){
#   print(trait_evolution_plot(exp_100_trait, what, paste("exp_100", what)))
# }
# 
# evolution_plots("mean_k")
# evolution_plots("std_k")
# evolution_plots("std_e_0")
# evolution_plots("num_winners")
# evolution_plots("mean_maturation")
# evolution_plots("contest_energy")
# evolution_plots("search_energy")
# evolution_plots("occupying_energy")
# evolution_plots("mean_exploration")
# evolution_plots("std_exploration")
```

### 2016-04-04 scrap/generation_comparison.Rmd
fixed r v data, integrated into remake

---
title: "A Comparison of Different Generation lengths"
author: "John"
date: "19 February 2016"
output: pdf_document
---
I ran one simulation stepping by 100 for 500 generations.
and another stepping by 250 for 2000 generations.

```{r}
library(jsonlite)
library(plyr)
library(ggplot2)
source("~/Documents/contests_model/R/load_datasets.R")
source("~/Documents/contests_model/R/make_plots.R")
cm_100 <- load_population("~/Documents/contests_model/data/cm_100/")
cm_2k <- load_population("~/Documents/contests_model/data/cm_2k/")

@@

population_plots <- function (x, y, limits){
  print(
    pop_values(cm_100, x = x, y = y, paste("cm_100",x, y)) + 
      scale_y_continuous(limits = limits)
  )
  print(
    pop_values(cm_2k, x = x, y = y, paste("cm_2k",x, y)) + 
      scale_y_continuous(limits = limits)
  )
}
e_0_limits <- get_limits("e_0", rbind(cm_2k, cm_100))
k_limits <- get_limits("k", rbind(cm_2k, cm_100))
```

There seems to be coexistence of strategies after a certain density is reached.
Where to next?

Test different parameters maybe?
I am running it with lower a lower logit coeff for the winner swap...

How to limit the aggression drift when training on a lot of generations?
Different commitment functions?
Different escalation curves?

```{r}
population_plots("log(N / patch_area)", "e_0", e_0_limits)
population_plots("log(N / patch_area)", "k", k_limits)
population_plots("patch_area", "e_0", e_0_limits)
population_plots("patch_area", "k", k_limits)
```

>>>>

---
title: "A Comparison of Different Generation lengths"
author: "John"
date: "19 February 2016"
output: html_document
---
I ran one simulation stepping by 100 for 500 generations.
and another stepping by 250 for 2000 generations.

```{r}
library(jsonlite)
library(plyr)
library(ggplot2)
source("~/Documents/contests_model/R/load_datasets.R")
source("~/Documents/contests_model/R/make_plots.R")
cm_100 <- load_population("~/Documents/contests_model/data/cm_100/")
cm_2k <- load_population("~/Documents/scrap/contest_data/6k/")
low_logit <- load_population("~/Documents/contests_model/data/low_logit/")
low_logit_100 <- load_population("~/Documents/contests_model/data/low_logit_100/")
repeated <- load_population("~/Documents/scrap/contest_data/repeated/")

@@

population_plots <- function (x, y, limits){
  print(
    pop_values(cm_100, x = x, y = y, paste("cm_100",x, y)) + 
      scale_y_continuous(limits = limits)
  )
  print(
    pop_values(cm_2k, x = x, y = y, paste("cm_6k",x, y)) + 
      scale_y_continuous(limits = limits)
  )
    print(
    pop_values(low_logit_100, x = x, y = y, paste("low_logit_100",x, y)) + 
      scale_y_continuous(limits = limits)
  )
      print(
    pop_values(low_logit, x = x, y = y, paste("low_logit",x, y)) + 
      scale_y_continuous(limits = limits)
  )
}
e_0_limits <- get_limits("e_0", rbind(cm_2k, cm_100, low_logit_100, low_logit))
k_limits <- get_limits("k", rbind(cm_2k, cm_100, low_logit_100, low_logit))
```

The low_logit graphs are those that have a the coef in the logistic of swapping = 1 compared to 10 in the cm ones,

some interesting co-existance,
but the same scattering problem...

```{r, dev='png'}
population_plots("log(N / patch_area)", "e_0", e_0_limits)
population_plots("log(N / patch_area)", "k", k_limits)

population_plots("patch_area", "e_0", e_0_limits)
population_plots("patch_area", "k", k_limits)
```
